---
title: "Data Manipulation"
author: "Jeff Goldsmith"
date: "`r Sys.time()`"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import data.

```{r csv}
library(tidyverse)

litters_data = read_csv(here::here("data", "FAS_litters.csv"),
  col_types = "ccddiiii")
litters_data = janitor::clean_names(litters_data)

pups_data = read_csv(here::here("data", "FAS_pups.csv"),
  col_types = "ciiiii")
pups_data = janitor::clean_names(pups_data)
```

## Select

Illustrating `select`.

```{r}
select(litters_data, group, litter_number, gd_of_birth)

select(litters_data, group, litter_number, gd_of_birth:pups_dead_birth)

select(litters_data, litter_number, gd18_weight, everything())

select(litters_data, -gd18_weight)

select(litters_data, starts_with("gd"))

pull(litters_data, group)
```


## Filter

Illustrating `filter`.

```{r}
filter(litters_data, group == "Mod7")

filter(litters_data, group == "Mod7", gd_of_birth == 19)

filter(litters_data, group %in% c("Mod7", "Con7"))

```

## Mutate

Illustrating `mutate`.


```{r}
mutate(litters_data,
       weight_gain = gd18_weight - gd0_weight,
       group = tolower(group))
```

## Arrange

Illustrating `arrage`.


```{r}
arrange(litters_data, gd0_weight)
```

## Piping

What is this pipe business?

```{r}
litters_data = 
  read_csv(here::here("data", "FAS_litters.csv"), 
                      col_types = "ccddiiii") %>% 
  janitor::clean_names() %>% 
  select(., -pups_survive) %>% 
  mutate(., 
    wt_gain = gd18_weight - gd0_weight,
    group = tolower(group))
```

Fitting a model as part of a pipe.

```{r}
litters_model = 
  litters_data %>% 
  filter(group %in% c("con7", "con8")) %>% 
  lm(gd18_weight ~ gd0_weight, data = .) 
```

## Other stuff

Tidy the output of a liner model (note: works with tons of model types).

```{r}
broom::tidy(litters_model) %>% 
  select(-std.error, -statistic) %>% 
  filter(term != "(Intercept)") %>% 
  knitr::kable(digits = 3)
```

Adding fitted values, residuals, etc.

```{r}
litters_data %>% 
  filter(group %in% c("con7", "con8")) %>% 
  modelr::add_predictions(model = litters_model) %>% 
  modelr::add_residuals(model = litters_model)
```


Adding predictions / residuals works even on different datasets -- handy for assessing prediction accuracy ...

```{r}
litters_data %>% 
  modelr::add_predictions(model = litters_model) %>% 
  modelr::add_residuals(model = litters_model)
```


